Estimating Uncertainty for Tipping Points with Deep Learning

### 2022-05-12 manuscript/manuscript.Rmd
missed one

```{r fig.cap="Forecasts of the Hopf bifurcation under each model"}
forecasts |> filter(simulation=="hopf", reps == 1, group == 1) |> 
  ggplot(aes(t, col=type, fill=type)) + 
  geom_ribbon(aes(ymin = lower, ymax = upper), alpha=0.5) +
  geom_ribbon(aes(ymin = lower, ymax = upper), alpha=0.5, data = hopf_sims) +
  geom_line(aes(y=mean)) +
  geom_line(aes(y=mean), data = hopf_obs) +
  facet_grid(forecasting_model ~ variable, scales = "free") +
  theme_bw() + 
  ggtitle("Hopf bifurcation")
```

>>>>

```{r fig.cap="Forecasts of the Hopf bifurcation under each model"}
forecasts |> filter(simulation=="hopf", reps == 1, group == 1) |> 
  ggplot(aes(t, col=type, fill=type)) + 
  geom_ribbon(aes(ymin = lower, ymax = upper), alpha=0.5) +
  geom_ribbon(aes(ymin = lower, ymax = upper), alpha=0.5, data = hopf_obs) +
  geom_line(aes(y=mean)) +
  geom_line(aes(y=mean), data = hopf_obs) +
  facet_grid(forecasting_model ~ variable, scales = "free") +
  theme_bw() + 
  ggtitle("Hopf bifurcation")
```
